---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
df <- read.table("C:/Users/DELL/Desktop/85-20data-new.txt",header=TRUE,sep=",")

#library(dplyr)
#library(magrittr)
#library(ggplot2)
#library(ggthemes)
#library(reshape2)

#df$X2.A

#df$X2.A<-data.frame(lapply(df$X2.A, function(x) as.numeric(gsub("\\%", "", x))/100))

#问题1
par(mfrow=c(1,5))
#①球队场均得分与胜率
revelant <- lm(df$PTS ~ df$WR,data = df)
summary(revelant)
cor(df$PTS,df$WR)#回归系数
plot(df$PTS,df$WR)
abline(revelant)

#②球队投篮命中率与胜率
revelant <- lm(df$ALL.A ~ df$WR,data = df)
summary(revelant)
cor(df$ALL.A,df$WR)
plot(df$ALL.A,df$WR)
abline(revelant)

#③球队投篮命中率与场均得分
revelant <- lm(df$ALL.A ~ df$PTS,data = df)
summary(revelant)
cor(df$ALL.A,df$PTS)
plot(df$ALL.A,df$PTS)
abline(revelant)

#④球队出手次数与场均得分
revelant <- lm(df$ALL.S ~ df$PTS,data = df)
summary(revelant)
cor(df$ALL.S,df$PTS)
plot(df$ALL.S,df$PTS)
abline(revelant)

#⑤球队罚球命中率与胜率
revelant <- lm(df$FT.A ~ df$WR,data = df)
summary(revelant)
cor(df$FT.A,df$WR)
plot(df$FT.A,df$WR)
abline(revelant)

#问题2
syear <- unique(df$Season)
both_pts5_wr5 <- data.frame( Season=rep(NA,35),
                           both_count=rep(NA,35))

rela_pts5_wr5 <- function(S){
  #根据赛季，取出数据
  #S <- "85-86"
  #print(S)0
  #print(df$Season)
  data_need_1 <- df[df$Season==S,]
  #print(S)
  #查看该赛季得分前5
  pts5 <- data_need_1[order(-data_need_1$PTS),]
  pts5 <- pts5[1:5,]
  #查看该赛季胜率前5
  wr5 <- data_need_1[order(-data_need_1$WR),]
  wr5 <- wr5[1:5,]
  #寻找得分胜率均在前5的球队
  both_count=0
  for(i in 1:5){
    #print(i)
    for(j in 1:5){
      #print(j)
      #print(pts5[i,'TEAM'])
      #print(wr5[j,'TEAM'])
      if(pts5[i,'TEAM']==wr5[j,'TEAM']){
        both_count <- both_count + 1
      }
      #print(both_count)
    }
  }
  return (both_count)
}

for (z in 1:length(syear)){
  #print(z)
  Season <- syear[z]
  #print(Season)
  both_pts5_wr5[z,'both_count'] <- rela_pts5_wr5(Season)
  both_pts5_wr5[z, 'Season'] <- Season
  #print(both_pts5_wr5[z,'both_count'])
}

#df[df$SeasonEnd==S,]
#df$SeasonEnd
#pts5
both_pts5_wr5

#问题3
plot_pts_wr <- function(TEAM){
  # TEAM <- "Los Angeles Lakers"
  #根据球队，选取数据
  data_need_2 <- df[df$TEAM==TEAM,]
  #画出得分随时间变化散点图
  plot(data_need_2$Season,data_need_2$PTS,pch=15,
       col="DarkTurquoise",xlim = c(0,35),ylim=c(70,130),xaxt="n")
  lines(data_need_2$PTS,col="DarkTurquoise",lty=1)#lty=1表示用实线连起来
  axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度
  #画出胜率随时间变化散点图
  plot(data_need_2$Season,data_need_2$WR,pch=16,
       col="DeepPink",xlim = c(0,35),ylim=c(0,1),xaxt="n")  #连线
  lines(data_need_2$WR,col="DeepPink",lty=2) #lty=2表示用虚线连起来
  axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度
  }
options(warn = -1)
#options(warn = 1)
plot_pts_wr("Los Angeles Lakers")

# library(ggplot2)
# ggplot(data_need_2, aes(Season, PTS)) + 
#   geom_point()
# 
# data_need_2$Season <- as.character(data_need_2$Season)
# data_need_2$Season <- factor(data_need_2$Season)
# plot(data_need_2$Season,data_need_2$PTS, type='l')
# ?plot
# length(data_need_2$Season)
# num <- as.character(1:35)
# plot(num,data_need_2$PTS, type='l')
# plot(num,data_need_2$PTS,pch=15,
#      col="DarkTurquoise",xlim = c(0,35),ylim=c(70,130),xaxt="n")
# lines(data_need_2$PTS,col="DarkTurquoise",lty=1)#lty=1表示用实线连起来
# axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度





#问题4
  syear <- unique(df$Season)
  league_data <- data.frame( Season=rep(NA,35),
                             PTS=rep(NA,35),
                             X2.S=rep(NA,35), 
                             X3.S=rep(NA,35),
                             FT.S=rep(NA,35))
  
  for (i in 1:length(syear)){
    #求联盟场均得分、两分球出手数、三分球出手数的均值
     Season <- syear[i]
     #按赛季选取数据
     data_need_3 <- df[df$Season==Season,]
     league_data[i,'Season'] <- Season
     league_data[i,'PTS'] <- mean(data_need_3$PTS)
     league_data[i,'X2.S'] <- mean(data_need_3$X2.S)
     league_data[i,'X3.S'] <- mean(data_need_3$X3.S)
     league_data[i,'FT.S'] <- mean(data_need_3$FT.S)
     
  }
  par(mfrow=c(1,3))
  #画出联盟场均得分随时间变化散点图
  plot(league_data$Season,league_data$PTS,pch=15,col="DarkTurquoise",
       xlim=c(0,35),ylim=c(80,120),
       xlab = "season",ylab="联盟场均得分",xaxt="n")
  lines(league_data$PTS,col="DarkTurquoise",lty=1)#lty=1表示用实线连起来
  axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度
  
  
  #画出罚球出手数随时间变化散点图
  plot(league_data$Season,league_data$FT.S,pch=18,col="purple",
       xlim=c(0,35),ylim=c(20,32),
       xlab = "season",ylab="联盟场均罚球",xaxt="n")
  lines(league_data$FT.S,col="purple",lty=1)#lty=1表示用实线连起来
  axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度
  
  
  #画出联盟两分球出手数随时间变化散点图
  plot(league_data$Season,league_data$X2.S,pch=16,col="DeepPink",
       xlim=c(0,35),ylim=c(0,100),
       xlab = "season",ylab= "两分球/三分球出手数",xaxt="n")
  lines(league_data$X2.S,col="DeepPink",lty=2) #lty=2表示用虚线连起来
  axis(1,league_data$Season,at=1:35,las=3)    #设置X轴坐标刻度
  
  #画出联盟三分球出手数随时间变化散点图
  points(league_data$Season,league_data$X3.S,pch=17,col="RosyBrown",cex=1)
  lines(league_data$X3.S,col="RosyBrown",lty=3) #lty=3表示用点线连起来
  #图例说明
 legend(15,100,c("X2.S","X3.S"),col=c("DeepPink","RosyBrown"),text.col=c("DeepPink","RosyBrown"),pch=c(16,17),lty=c(2,3),xpd = TRUE)
  

  
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
